SunPy - Python for Solar Physics

### 2014-01-22 2-2-Lightcurve.tex
more changes

\begin{listing}[H]
\begin{minted}{python}
>>> print lyra.data
<class 'pandas.core.frame.DataFrame'>
DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
2011-01-28 23:59:59.983993
Data columns (total 4 columns):
CHANNEL1    1496629  non-null values
CHANNEL2    1496629  non-null values
CHANNEL3    1496629  non-null values
CHANNEL4    1496629  non-null values
dtypes: float64(4)

>>> print lyra.data.index
<class 'pandas.tseries.index.DatetimeIndex'>
[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
Length: 1496629, Freq: None, Timezone: None
\end{minted}
\label{lyra_pandas}
\caption{Accessing the data and time axis in a Lightcurve}
\end{listing}

>>>>

\begin{listing}[H]
\begin{minted}{python}
>>> print lyra.data
<class pandas.core.frame.DataFrame>
DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
2011-01-28 23:59:59.983993
Data columns (total 4 columns):
CHANNEL1    1496629  non-null values
CHANNEL2    1496629  non-null values
CHANNEL3    1496629  non-null values
CHANNEL4    1496629  non-null values
dtypes: float64(4)

>>> print lyra.data.index
<class pandas.tseries.index.DatetimeIndex>
[2011-01-28 00:00:00.110000, ..., 2011-01-28 23:59:59.983993]
Length: 1496629, Freq: None, Timezone: None
\end{minted}
\label{lyra_pandas}
\caption{Accessing the data and time axis in a Lightcurve}
\end{listing}

### 2014-01-22 6-Future.tex
Fix merge related issues
More post-merge changes
more changes

\section{Future of SunPy}
SunPy as a project has existed for roughly three years. In this time the code 
base has grown to over $110,000$ lines. SunPy in it's current form is a useful 
package for the analysis of calibrated solar data, however, the code base is 
still very changeable from release to release.

The near-term future of the SunPy library is likely to continue this changeable 
nature with re-factoring and restructuring planned, especially within the 
core data types. The main focus upon the data types defined inside sunpy is to 
improve the interoperability and to redesign them in a more consistent manner.

In the past 12 months the collaboration with the Astropy project 
\cite{theastropycollaboration2013} has grown. The future of SunPy 
will continue this collaboration as the Astropy package provides many core 
tools that are applicable to all types of astronomy. For example the 
\texttt{astropy.units} submodule provides a simple and efficient way of 
representing physical units in Python data types, there are plans to 
incorporate this widely in the SunPy code-base.

>>>>

\section{Future of SunPy}
SunPy as a project has existed for roughly three years. In this time the code 
base has grown to over 110,000 lines. SunPy in it's current form is a useful 
package for the analysis of calibrated solar data, however, the code base is 
still very changeable from release to release.

As discussed in Section \ref{sec:Intro}, the primary focus of the 
\texttt{sunpy} library is the analysis and visualisation of `high level' solar 
data. This means data that has been put through instrument processing and 
calibration routines, and contains full (WCS) coordinate information. The 
development plan for SunPy is to continue development within this scope. The 
primary components of this plan are to provide a set of data types that are 
interchangeable with one another, \textit{i.e.} if you slice a \texttt{MapCube} 
along one coordinate a \texttt{LightCurve} of intensity along the time range of 
the \texttt{MapCube} should be returned. To achieve this goal all the data 
types need to share a unified coordinate system architecture so that each data 
type is aware of what the physical type of it's data is and how operations on 
that data should be performed.

In concert with the work on the data types further integration with the 
\texttt{astropy} package will enable SunPy to inherit the large amounts of work 
done in that project to support a platform for astronomical data analysis. For 
example the \texttt{astropy.units} submodule provides a simple and efficient 
way of representing physical units in Python data types, there are plans to 
incorporate this widely in the SunPy code-base. In the past 12 months the 
collaboration with the Astropy project \cite{theastropycollaboration2013} and 
it's community has grown, this direct collaboration between Astropy and 
SunPy will be one of the key strengths of SunPy going forward.
